%-------------------------
% Resume in Latex
% Author : Sindhu Yasa
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
% Define \titrule for section formatting
\newcommand{\titrule}{\rule[0.5ex]{\linewidth}{1pt}}
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titrule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-10pt}\item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{1pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Sindhu Yasa} \\ \vspace{1pt}
    \small 706-593-8457 $|$ \href{mailto:sindhu.yasa06@gmail.com}{\underline{sindhu.yasa06@gmail.com}} $|$ 
    \href{https://linkedin.com/in/sindhu-yasa}{\underline{linkedin.com/in/sindhu-yasa}} $|$
    \href{https://github.com/sindhu-yasa}{\underline{github.com/sindhu-yasa}}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\vspace{-8pt}
Applied Computer Science Master’s graduate and Full-Stack Developer specializing in building responsive, scalable web applications. Proficient in modern JavaScript frameworks (React, Next.js), backend architecture (Python/Flask, Java/Spring Boot), and cloud integration (AWS). Experienced in optimizing enterprise workflows and bridging technical research with production-ready software solutions.

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\vspace{-8pt}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    
     \textbf{Languages}{: Java, Python, C, JavaScript, TypeScript, SQL, HTML, CSS, C\#} \\
     \textbf{Frameworks}{: React JS, Next.js, Bootstrap, Tailwind CSS, Zustand (State Management), Node.js, Flask, Django, Spring Boot, RESTful APIs.} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, scikit-learn, TensorFlow, Keras, Plotly} \\
     \textbf{Databases}{: MySQL, PostgreSQL, MongoDB} \\
     \textbf{Other}{: AWS, Azure, Git, Jenkins, ServiceNow, SAP}\\
     \textbf{Game Dev} {: Unity 2D/3D, Vuforia AR, C\# Scripting, Game Logic Design, Asset \& Scene Management, 2D/3D Physics, Quality Assurance (QA) Testing, and Cross-Platform Building } 
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\vspace{-15pt}
\resumeSubHeadingListStart
\resumeSubheading
{Research Intern}{Jul. 2025 -- Present}
{Columbus State University, TSYS School of Computer Science}{Columbus, GA}
\resumeItemListStart
    \resumeItem{Architected and developed an AR-based Java learning platform using \textbf{Unity and Vuforia}, implementing marker-based tracking to visualize complex Object-Oriented Programming (OOP) concepts.}
    \resumeItem{Designed a modular system for interactive 3D simulations, streamlining the integration of complex logic for beginner programmers.}
    \resumeItem{Refined application performance through iterative user testing and feedback loops, optimizing asset rendering and scene transitions for mobile deployment.}
    \resumeItem{Presented technical milestones at university-led events, demonstrating the intersection of \textbf{Spatial Computing} and educational technology to faculty and industry stakeholders.}
\resumeItemListEnd

  \resumeSubheading
    {Operations Executive}{Dec. 2021 -- July 2023}
    {CYIENT}{Hyderabad, India}
    \resumeItemListStart
      \resumeItem{Worked with \textbf{ServiceNow}, \textbf{SAP}, and INX to support and optimize enterprise operational workflows.}
      \resumeItem{Managed incident tickets, change requests, and service tasks ensuring SLA compliance.}
      \resumeItem{Performed data audits and root cause analysis to maintain system data integrity.}
      \resumeItem{Generated reports and contributed to dashboard updates for internal stakeholders.}
      \resumeItem{Collaborated with client (\textbf{Rio Tinto}) and cross-functional teams to resolve real-time issues.}
      \resumeItem{Automated repetitive workflows and improved process efficiency.}
      \resumeItem{Trained and mentored \textbf{10+ new hires}; created SOPs and documentation.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\vspace{-15pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Columbus State University}{Columbus, GA}
      {Master of Science in Applied Computer Science, Software Development Track}{Aug. 2023 -- May 2025}
      \vspace{-10pt}
    \resumeSubheading
      {Ideal Degree College for Women}{Hyderabad, India}
      {Bachelor of Science in Mathematics, Statistics, Computer Science; GPA: 8.82}{Completed May 2021}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\vspace{-5pt}

    \resumeSubHeadingListStart

\resumeProjectHeading
          {\textbf{Art Gallery Affinity} $|$ \emph{React JS, Zustand, Art Institute of Chicago API}}{Apr. 2024}
          \resumeItemListStart
            \resumeItem{Built an interactive UI using React JS and Zustand for exploring public art collections via REST API.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Bank Loan Application Portal} $|$ \emph{Python, Flask, Object-Oriented Design}}{Dec. 2023}
          \resumeItemListStart
            \resumeItem{Developed a secure web application for clients and employees to manage loan applications using OOD.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Smart Course Planner} $|$ \emph{Python, Directed Acyclic Graphs}}{Dec. 2023}
          \resumeItemListStart
            \resumeItem{Designed an academic planning tool using DAGs to manage course prerequisites and sequencing.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{PopUp Java – Game-Based Learning Platform} $|$ \emph{Unity, Vuforia, AR, Android, C\#}}{Feb. 2026}
          \resumeItemListStart
            \resumeItem{Developed a Unity-based educational game using Vuforia and Android AR for marker-anchored augmented reality.}
            \resumeItem{Integrated multiple AR prefab simulations (robot, dog, tree) as interactive modules to reinforce Java concepts.}
            \resumeItem{Packaged and built a Windows executable and began developing mobile and web-friendly versions.}
          \resumeItemListEnd

    \resumeProjectHeading
{\textbf{Egg Rush – 2D Arcade Game} $|$ \emph{Unity, C\#, 2D Physics, Sprite Animation}}{Jan. 2026}
\resumeItemListStart
    \resumeItem{Developed a 2D arcade game featuring dynamic object spawning and collision-based scoring mechanics.}
    \resumeItem{Implemented responsive player controls and optimized 2D physics for smooth character movement and interaction.}
    \resumeItem{Managed game state transitions including start menus, game-over loops, and high-score persistence using C\#.}
\resumeItemListEnd


      \resumeProjectHeading
          {\textbf{CSUBatch Scheduling System} $|$ \emph{Java, Multithreading, Scheduling Algorithms}}{May 2025}
          \resumeItemListStart
            \resumeItem{Developed a command-line scheduling system with FCFS, SJF, and Priority Scheduling algorithms.}
            \resumeItem{Implemented multithreading with mutex locks for thread safety and created a thread-safe job queue.}
            \resumeItem{Led performance testing with JUnit to evaluate metrics like turnaround time and throughput.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Walmart Retail Sales Forecasting} $|$ \emph{Python, XGBoost, Random Forest, PCA}}{Dec. 2024}
          \resumeItemListStart
            \resumeItem{Built a predictive model using a dataset of 421,570 entries from 45 stores under Dr. Rania Hodhod.}
            \resumeItem{Performed extensive preprocessing: date decomposition, holiday encoding, and PCA-based feature reduction.}
            \resumeItem{Trained and evaluated models including Random Forest and XGBoost; achieved least RMSE using lag features.}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Licenses \& Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Microsoft 365 Certified: Fundamentals} $|$ Microsoft (June 2025) \\
     \textbf{SAP Certified Application Associate} $|$ SAP, Cyient (May 2022) \\
     \textbf{Introduction to Programming in Python / Java} $|$ Udemy (2024)
    }}
 \end{itemize}

%-------------------------------------------
\end{document}